---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ghtraffic

<!-- badges: start -->
<!-- badges: end -->

The goal of ghtraffic is to access github traffic data using github api.

## Installation

Development version from [GitHub](https://github.com/) with:

```{r installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("kvasilopoulos/ghtraffic")
```

# Usage

Make sure you have the necessary setup with github user and token.
```{r load gh}
library(gh)
gh_whoami()
```

And the you can send the request to find the traffic data for the `ghtraffic` repo from the `kvasilopoulos` user.
```{r load ghtraffic}
library(ghtraffic)
repo_traffic("kvasilopoulos", "ghtraffic")
```

## Next Steps

Build on infrastructure to be able to set up a tracker into the repo, in order to be able to track traffic data for more than 2 weeks.

---

Please note that the 'ghtraffic' project is released with a
  [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms

